---
title: "ecar"
author: "Kar"
date: '2022-06-23'
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
    number_sections: true
  github_document:
    toc: yes
    toc_depth: 4
always_allow_html: yes
---

# R PACKAGES LOADED

```{r, message=FALSE, warning=FALSE}

library(data.table)
library(tidyverse)
library(kableExtra)
library(skimr)

```

# INTRODUCTION

This project will apply an intensive list of statistical analyses on a electrical car dataset to understand about electric cars.

# DATA PREPARATION

Dataset used in this project is a public dataset available on Kaggle, visit this [link](https://www.kaggle.com/datasets/geoffnel/evs-one-electric-vehicle-dataset) to the relevant page. The dataset has been downloaded as a csv format and will be imported in next section. 

## Data Import

This section imports the dataset.

```{r}
ecar <- read.csv("ElectricCarData_Norm.csv")

```

Following is the row dataset.

```{r}
data.table(ecar)
```

## Data Description

```{r}
No. <- c(1:14)

Variables <- c("Brand", 
               "Model", 
               "AccelSec",
               "TopSpeed_KmH",
               "Range_Km",
               "Efficiency_WhKm",
               "FastCharge_KmH",
               "RapidCharge",
               "PowerTrain",
               "PlugType",
               "BodyStyle",
               "Segment",
               "Seats",
               "PriceEuro")

Description <- c("Manufacturer of the vehicle",
                 "Model name",
                 "Acceleration as 0-100 km/h",
                 "The top speed in km/h",
                 "Range in km",
                 "Efficiency Wh/km",
                 "Charge km/h",
                 "Yes / No",
                 "Front, rear, or all wheel drive",
                 "Plug type",
                 "Basic size or style",
                 "Market segment",
                 "Number of seats",
                 "Price in Germany before tax incentives")


data.frame(No. , Variables, Description) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("bordered", "striped", "hover"), 
                full_width = F,
                position = "left") %>% 
  row_spec(0, angle = -2)


```



## Data exploration

**1. Data structure**

There are 103 rows of data in the dataset and 14 columns of variables. 

```{r}
glimpse(ecar)

```

* 12 columns are characters but mostly should be numerical such as Accel, TopSpeed, Range, Efficiency, and FastCharge.  

* 2 columns are integers but the "Seats" variables should be converted to factor type. 

* Many of the character type variables will need to be converted into factor for their categorical nature. 

**2. Missing values**

There are no missing values in the dataset.

```{r}
colSums(is.na(ecar))

```


# DATA CLEANING

## Numeric Conversion

Following codes rename the variables that need to be numerical and remove the units in their values to allow structural conversion from character to numerical. They are:

* Accel_sec    
* TopSpeed_KmH  
* Range_KmH  
* Efficiency_WhKm  
* Fastcharge_KmH  

```{r}
ecar2 <- ecar %>%
  rename("Accel_sec" = "Accel",
         "TopSpeed_KmH" = "TopSpeed",
         "Range_Km" = "Range",
         "Efficiency_WhKm" = "Efficiency",
         "Fastcharge_KmH" = "FastCharge") %>% 
  mutate(Accel_sec = str_remove(Accel_sec, "sec"),
         TopSpeed_KmH = str_remove(TopSpeed_KmH, "km/h"),
         Range_Km = str_remove(Range_Km, "km"),
         Efficiency_WhKm = str_remove(Efficiency_WhKm, "Wh/km"),
         Fastcharge_KmH = str_remove(Fastcharge_KmH, "km/h"),
         # numerical conversion
         Accel_sec = as.numeric(Accel_sec),
         TopSpeed_KmH = as.numeric(TopSpeed_KmH),
         Range_Km = as.numeric(Range_Km),
         Efficiency_WhKm = as.numeric(Efficiency_WhKm),
         Fastcharge_KmH = as.numeric(Fastcharge_KmH)) 

```

From the warning, some NAs has been induced to the variable "Fastcharge_KmH". 5 NAs has been introduced from following output. 

```{r}
colSums(is.na(ecar2))
```

Investigating the reason by first searching for the indexes of these NAs.

```{r}
which(is.na(ecar2$Fastcharge_KmH))

```
Targeting the respect index of original dataset and found the reasons that "-" has been given to these values instead of numbers. 

```{r}
slice(ecar, c(58, 69, 78, 83, 92))

```

Because there are only 5 missing values, and their proportion will not affect the statistics significantly, therefore I will just them.

```{r}
ecar2 <- na.omit(ecar2)

```

## RapidCharge Yes/No

Here will remove the variable "RapidCharge" from the dataset because it has only 1 value, which is "Rapid charging possible" and this variable will add no value to the analysis. 

```{r}
unique(ecar2$RapidCharge) 
```

```{r}
ecar2 <- ecar2 %>% dplyr::select(-RapidCharge)
```


## PowerTrain Rename

This section change the category names of the variable "PowerTrain" to a shorter version. The categories are:

```{r}
unique(ecar2$PowerTrain)
```
They will be changed to "AWD", "RWD, and "FWD" accordingly. 

```{r}
ecar2 <- ecar2 %>% 
  mutate(PowerTrain = fct_recode(PowerTrain, 
                                 "AWD" = "All Wheel Drive",
                                 "RWD" = "Rear Wheel Drive",
                                 "FWD" = "Front Wheel Drive"))


```

Now the conversion has been completed. 

```{r}
unique(ecar2$PowerTrain)

```


## Triming

This section will remove leading and/or trailing white spaces of values in all character variables. For example, looking at the first value of the variable "Brand", the "Tesla " has a trailing space to be removed. 

```{r}
str(ecar2)
```

Following operation completes the task.

```{r}
ecar2 <- ecar2 %>% 
  mutate_if(is.character, trimws)

str(ecar2)

```



## Factor Conversion & rearrangement

This section will convert character variables or discrete variable (numeric) that has categorical nature into factor.

These variables are:

* Brand  
* PlugType  
* BodyStyle  
* Segment  
* Seats  

At the same time, these variables will be shifted forward and relocated after the variable "Model". 

```{r}
ecar2 <- ecar2 %>% 
  mutate(Brand = as.factor(Brand),
         PlugType = as.factor(PlugType),
         BodyStyle = as.factor(BodyStyle),
         Segment = as.factor(Segment),
         Seats = as.factor(Seats)
         ) %>% 
  relocate(c("PowerTrain", "PlugType", "BodyStyle", "Segment", "Seats"), .after = "Model")
  


```


## Variables removal

This project will work on statistical analysis and the variable "Brand" will give no value to the analysis because there are 98 rows and yet almost all of the row has its own model label. 

Additionally, the variable "segment" will also be removed. It stands for "Market segment". It is irrelevant to the other variables in the dataset. 

```{r}
unique(ecar2$Model)

```
Removing the "Model" variable:

```{r}
ecar2 <- ecar2 %>% 
  dplyr::select(-Model, -Segment)

```

Now the variables should be cleaned and ready for analysis. 

```{r}
glimpse(ecar2)
```

# Statistical Summary

Examining the values of variables in the dataset. 

```{r}

data.frame(unclass(summary(ecar2, maxsum = 40)), 
           check.names = F, 
           stringsAsFactors = T) %>% 
  remove_rownames()

```

```{r}
glimpse(ecar2)
```




