---
title: "ecar"
author: "Kar"
date: '2022-06-23'
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  github_document:
    toc: yes
    toc_depth: 4
always_allow_html: yes
---

## R library

```{r, message=FALSE, warning=FALSE}

library(data.table)
library(tidyverse)
library(kableExtra)

```

## INTRODUCTION

This project will apply an intensive list of statistical analyses on a electrical car dataset to understand about electric cars.

## DATA PREPARATION

Dataset used in this project is a public dataset available on Kaggle, visit this [link](https://www.kaggle.com/datasets/geoffnel/evs-one-electric-vehicle-dataset) to the relevant page. The dataset has been downloaded as a csv format and will be imported in next section. 

### DATA IMPORT

This section imports the dataset.

```{r}
ecar <- read.csv("ElectricCarData_Norm.csv")

```

Following is the row dataset.

```{r}
data.table(ecar)
```

### DATA DESCRIPTION


```{r}
Variables <- c("Brand", 
               "Model", 
               "AccelSec",
               "TopSpeed_KmH",
               "Range_Km",
               "Efficiency_WhKm",
               "FastCharge_KmH",
               "RapidCharge",
               "PowerTrain",
               "PlugType",
               "BodyStyle",
               "Segment",
               "Seats",
               "PriceEuro")

Description <- c("Manufacturer of the vehicle",
                 "Model name",
                 "Acceleration as 0-100 km/h",
                 "The top speed in km/h",
                 "Range in km",
                 "Efficiency Wh/km",
                 "Charge km/h",
                 "Yes / No",
                 "Front, rear, or all wheel drive",
                 "Plug type",
                 "Basic size or style",
                 "Market segment",
                 "Number of seats",
                 "Price in Germany before tax incentives")


data.frame(Variables, Description) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("bordered", "striped"), full_width = F)


```



### DATA EXPLORATION
